---
title: "Case Study"
author: "Jiacheng Wu"
date: "10/22/2021"
output: github_document
---

```{r}
library(tidyverse)
library(p8105.datasets)
library(leaflet)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```


## Load a dataset

```{r}
data("nyc_airbnb")
nyc_airbnb
```

* Is price correlated with review score?
* How mant rentals are there? Of what type?
* Which neighborhood is the most popular? Most expensive?
* Which neighborhood has the highest review?
* Is availability related to neighborhood?
* Is length of stay related to neighborhood (borough)?

```{r}
nyc_airbnb = 
  nyc_airbnb %>% 
  mutate(stars = review_scores_location / 2) %>% 
  rename(borough = neighbourhood_group) 
```

Count things:

```{r}
nyc_airbnb %>% 
  count(borough, room_type) %>% 
  pivot_wider(
    names_from = room_type,
    values_from = n
  )
```


Price and roomtype...

```{r}
nyc_airbnb %>% 
  ggplot(aes(x = stars, y = price)) +
  geom_point() +
  facet_grid(. ~ room_type)
```

Price and neighborhood

```{r}
nyc_airbnb %>% 
  filter(borough == "Manhattan") %>% 
  group_by(neighbourhood) %>% 
  summarise(mean_price = mean(price, na.rm = TRUE)) %>% 
  arrange(mean_price)

nyc_airbnb %>% 
  filter(borough == "Manhattan",
         price <= 1000) %>% 
  mutate(neighbourhood = 
           fct_reorder(neighbourhood, price)) %>% 
  ggplot(aes(x = neighbourhood, y = price)) +
  geom_boxplot() +
  coord_flip() 
```

Price vs location

```{r}
nyc_airbnb %>% 
  filter(price < 500) %>% 
  sample_n(5000) %>% 
  ggplot(aes(x = lat, y = long, color = price)) +
  geom_point(alpha = .5)
```


## Retry leaflet

```{r, eval=FALSE}
nyc_airbnb %>% 
  leaflet() %>% 
  addTiles() %>% 
  addMarkers(~lat, ~long)
```







